Random Matrix Theory Tools for the Analysis of Functional Magnetic Resonance Imaging Examinations

### 2021-09-09 paper/latex/rmt.tex
get biblio working
get one citation working

Whether in the presence of experimental stimuli, or the relative absence, as in a resting state,
complex functional connectivity networks are ubiquitous [1]–[4]. This complexity suggests fMRI is a
candidate to be studied using Random Matrix Theory (RMT), a set of mathematical tools originally
developed some 50 years ago to solve complex problems in nuclear physics [5], [6]. In various
physical systems where nuclei can have different possible states, precisely modeling the entirety of
the interactions between nuclei is often intractable. For such large, complex systems, the
eigenvalues (or spectra) efficiently summarize the totality of the interactions between components
of the system, and RMT describes the expected behaviour of such eigenvalues. By analysing the
spectrum statistically, complex systems can be investigated by comparison to the universal
properties predicted by RMT.

@@

>>>>

Whether in the presence of experimental stimuli, or the relative absence, as in a resting state,
complex functional connectivity networks are ubiquitous
(\cite{bucknerBrainDefaultNetwork2008,foxCoverHumanBrain2005,gonzalez-castilloTaskbasedDynamicFunctional2018,hermundstadStructuralFoundationsRestingstate2013})
[1]–[4]. This complexity suggests fMRI is a candidate to be studied using Random Matrix Theory
(RMT), a set of mathematical tools originally developed some 50 years ago to solve complex problems
in nuclear physics [5], [6]. In various physical systems where nuclei can have different possible
states, precisely modeling the entirety of the interactions between nuclei is often intractable. For
such large, complex systems, the eigenvalues (or spectra) efficiently summarize the totality of the
interactions between components of the system, and RMT describes the expected behaviour of such
eigenvalues. By analysing the spectrum statistically, complex systems can be investigated by
comparison to the universal properties predicted by RMT.

@@

\section{References}
\printbibliography{}
